Kyoto VR MQP Paper First Draft

### 2019-09-25 paper.tex
finish deploying editour section

We were able to get shell access to the shared hosting environment, but without
superuser privileges. This meant we couldn't install packages, change system
settings, or access systemctl. In order to install Node.js and npm in this
environment we had to use Node Version Manager, a series of shell scripts that
handles downloading and compiling various versions of Node~\autocite{nvmsh2019}.
The only difficulty with this was finding a version of Node.js that could
compile with the older version of GCC the RHEL server had. Fortunately the
server already had git installed, so we were able to simply clone the backend
from GitHub and run it with npm.

However, the server already had Apache listening on port 80, and without
superuser privileges we could not edit the Apache configuration files to change
this. Instead we decided to configure Apache as a reverse proxy, using only the
rules that can be put in a \texttt{.htaccess} file, since this is the only
configuration file we could access. Using Apache's \texttt{mod\_rewrite} module
we were able to rewrite incoming requests on port 80 to instead go to
\texttt{localhost:3000}, the port Node.js was listening
on~\autocite{apache2019}.

>>>>

We were able to get shell access to the shared hosting environment, but without
superuser privileges. This meant we couldn't install packages, change system
settings, or access \texttt{systemctl}. In order to install Node.js and npm in
this environment we had to use Node Version Manager, a series of shell scripts
that handles downloading and compiling various versions of
Node~\autocite{nvmsh2019}.  The only difficulty with this was finding a version
of Node.js that could compile with the older version of GCC the RHEL server had.
Fortunately the server already had git installed, so we were able to simply
clone the backend from GitHub and run it with npm.

However, the server already had Apache listening on port 80, and without
superuser privileges we could not edit the Apache configuration files to change
this. Instead we decided to configure Apache as a reverse proxy, using only the
rules that can be put in a \texttt{.htaccess} file, since this is the only
configuration file we could access. Using Apache's \texttt{mod\_rewrite} module
we were able to rewrite incoming requests on port 80 to instead go to
\texttt{localhost:3000}, the port where Node.js was
listening~\autocite{apache2019}.

With no access to \texttt{systemctl} we could not use the custom systemd service
we wrote to manage the server daemon. Instead, we used a custom shell script and
an npm package called ``forever'' to handle starting and stopping it. The
forever package runs Node.js scripts continuously, automatically restarting them
if they crash~\autocite{robbins2019}.
